---
title: "Pseudo Absence Bayes Regs"
output: html_document
author: "Shannon Spragg"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Formatting our Pseudo-absence Bayesian Probability of Conflict Regressions:

This document will include the different Bayesian regression models (null and full) for our WARP pseudo-abs dataframe (1's = all conflict report points , 0's = randomly generated absence points).

We produce one primary full model to estimate the probability of any wildlife conflict points occurring. As we are demonstrating the probability of conflict for any species, we only include predictors that possibly pertain to all species (not bear specific) which are human population density, distance to nearest PA and metro area, density of ground crop farming and density of animal farming by CCS region, and a varying intercept for CCS region.

Model 1 (null) : logit(p_conflict) = 1 + a[CCS]
Model 2 (full) : logit(p_conflict) = a[CCS] + B_1*PopDens + B_2 * Dist2PA + B_3 * Dist2Metro + B_4 * AnimalFarmDensity + B_5 * GroundCropFarmDensity

We will use the resulting p(conflict) values to adjust our predictor rasters (multiplying the coefficients by each raster) and combine these rasters into a single raster representing our p(conflict) for general species. These values will then be extracted to points in our p(conflict) model for bears as a predictor.

## Bring in and Scale the Data:

```{r packages,echo=FALSE,include=FALSE}
library(sf)
library(tidyverse)
library(dplyr)
library(raster)
library(terra)
library(tidyverse)
library(caret)
library(GGally)
library(ggplot2)
library(corrplot)
library(bayesplot)
theme_set(bayesplot::theme_default(base_family = "sans"))
library(rstanarm)
options(mc.cores = 1)
library(loo)
library(projpred)
SEED=14124869
library(sjPlot)
library(nloptr)
library(sjmisc)
library(rsq)
library(tidybayes)
library(pROC)
library(bayestestR)
#install.packages("brms")
library(brms)
library(corrplot)
```


```{r data, echo=FALSE}
# Import Data: ------------------------------------------------------------
# Here we have our presence-absence data:
warp.pres.abs <- st_read("/Users/shannonspragg/ONA_GRIZZ/Data/processed/pres.abs.final.shp")
head(warp.pres.abs)

# Access this via googledrive: In our ONA-GRIZZ folder
# at the link: https://drive.google.com/drive/u/0/folders/17n64UwIiwhGVCwTQX8uc31ybWJ0YIdtv
```


```{r scale pres-abs variables, echo=FALSE}
# Scale the Variables: ----------------------------------------------------------
# Here we create a function to scale by subtracting the mean and dividing by 2 standard deviations:
scale2sd <-function(variable){(variable - mean(variable, na.rm=TRUE))/(2*sd(variable, na.rm=TRUE))}

dist.2.pa.ps <- scale2sd(warp.pres.abs$dst__PA)
dist.2.met.ps <- scale2sd(warp.pres.abs$dst_t_M)
pop.dens <- scale2sd(warp.pres.abs$Human_Dens)
animal.farm.dens.ps <- warp.pres.abs$Anml_Fr
ground.crop.dens.ps <- warp.pres.abs$Grnd_Cr

conflict_presence_ps <- warp.pres.abs$bears # Binomial bears --> for this data, 1's are all wildlife

warp.pres.abs$CCSNAME <- as.factor(warp.pres.abs$CCSNAME)

CCSNAME.ps <- warp.pres.abs$CCSNAME
```
We can write a scale function to center our predictors by subtracting the means and scaling by dividing by two times their standard deviation.

## Producing the Bayes Model:
```{r mini df, echo=FALSE}
# Fit Model with Rstanarm: ------------------------------------------------
# Make a mini data frame with just our general conflict predictors (no spatial info):
mini.warp.df.ps <-  data.frame(conflict_presence_ps, dist.2.pa.ps, dist.2.met.ps, animal.farm.dens.ps, ground.crop.dens.ps, CCSNAME.ps, pop.dens)

str(mini.warp.df.ps)
```
Here we produce a mini data frame that excludes the spatial geometry, but includes all of our critical predictors.

```{r models, echo=FALSE}
# Fitting our Posterior Regression: ---------------------------------------
# tutorial here: https://avehtari.github.io/modelselection/diabetes.html 

# Set our prior:
t_prior <- student_t(df = 7, location = 0, scale = 1.5)
int_prior <- normal(location = 0, scale = NULL, autoscale = FALSE)
# Build our posterior distribution: stan_glm returns the posterior dist for parameters describing the uncertainty related to unknown parameter values

# Start with our Null (Intercept-Only) Model:
post.int.only <- stan_glmer(conflict_presence_ps ~ 1 + (1 | CCSNAME.ps), 
                  data = mini.warp.df.ps,
                  family = binomial(link = "logit"), # define our binomial glm
                  prior = t_prior, prior_intercept = int_prior, 
                  iter = 5000,
                  seed = SEED, refresh=0) # we add seed for reproducability

# Global Model: including all of our predictors 
post.pa.full <- stan_glmer(conflict_presence_ps ~ dist.2.pa.ps + dist.2.met.ps + animal.farm.dens.ps + ground.crop.dens.ps + pop.dens + (1 | CCSNAME.ps), 
                            data = mini.warp.df.ps,
                            family = binomial(link = "logit"), # define our binomial glm
                            prior = t_prior, prior_intercept = int_prior, QR=TRUE,
                            seed = SEED, refresh=0) # we add seed for reproducability

summary(post.int.onlny)
summary(post.pa.full)

# Save an object to a file
saveRDS(post.pa.full, file = "/Users/shannonspragg/ONA_GRIZZ/Data/processed/post_pa_full.rds")
saveRDS(post.int.only, file = "/Users/shannonspragg/ONA_GRIZZ/Data/processed/post_pa_int.rds")

post.pa.full <- readRDS(file = "/Users/shannonspragg/ONA_GRIZZ/Data/processed/post_pa_full.rds")
post.int.only <- readRDS(file = "/Users/shannonspragg/ONA_GRIZZ/Data/processed/post_pa_int.rds")

plot_model(post.pa.full, sort.est = TRUE)

# Labeled Effect Plot:
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE
post.pa.full.effects.plot <- sjPlot::plot_model(post.pa.full, 
                                         axis.labels=c("Population Density", "Ground Crop & Produce Density (per km^2)", "Animal & Meat Farming Density (per km^2)" , "Distance to Metro Area (km)", "Distance to Protected Area (km)"),
                                         show.values=TRUE, show.p=FALSE,
                                         title="Effects of Social & Environmental Variables on General Conflict")

```
Here we set our initial priors to students t with 7 degrees of freedom, and a scale of 2.5 which is a reasonable default fir prior when coefficients should be close to zero but have some chance of being large. We build our two models using stan_glm to return our posterior distribution for the specified model parameters. Our first model is an intercept only (null) model which only includes our intercept and varying intercepts. It has the simple formula of logit(p_conflict) = conflict_presence ~ 1 + a[CCS]. Model 2, logit(p_conflict) = a[CCS] + B_1 * Dist2PA + B_2 * Dist2Metro + B_3 * AnimalFarming + B_4 * GroundCropFarming + B_5 * PopulationDensity.  

## Run a Variable Correlation Plot:
```{r correlation plot, echo=FALSE}
# Run Correlation Plot: ---------------------------------------------------

# Make a correlation matrix for our data dn predictors:
cor.matrix.df.ps <- data.frame(dist.2.pa.ps, dist.2.met.ps, animal.farm.dens.ps, ground.crop.dens.ps, pop.dens)

cor.matrix.ps <- cor(cor.matrix.df.ps)
round(cor.matrix.ps, 2)

# Make a plot with proportional circles on a diagonal, coefficent numbers, and legend at the bottom:
predictor.cor.plot.ps <- corrplot(cor.matrix.ps, type = 'lower', order = 'hclust', tl.col = 'black',addCoef.col = 'grey',
                               cl.ratio = 0.2, tl.srt = 45, col = COL2('PuOr', 10))
```
We see that there is some correlation between the two agriculture variables. However, if we remove one of these variables from the full model, it does not really impact results at all, so this is not a concern.

## Plotting Our Mixed Effects:
```{r mixed efffects, echo=FALSE}
# Plotting Marginal Effects:
plot_model(post.pa.full, type = "pred", title="Predicted Probabilities of General Conflict Presence",
           axis.labels=c("Conflict Presence", "Distance to PA" ,"Distance to Metro" ,"Dominant Farm Type", "Total Farm Count", "[Total Farm Count]^2", "Population Density" ))

plot_model(post.pa.full, type = "pred", terms = c("dist.2.pa.ps", "dist.2.met.ps", "pop.dens", "animal.farm.dens.ps", "ground.crop.dens.ps"))


# Basic Mixed Effect Plot:
sjPlot::plot_model(post.pa.full)

# Labeled Effect Plot:
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE
post1.effects.plot <- sjPlot::plot_model(post.pa.full, 
                   axis.labels=c("Population Density", "Ground Crop & Produce Farming Density","Animal & Meat Farming Density","Distance to Metro Areas (km)", "Distance to Protected Area (km)"),
                   show.values=TRUE, show.p=FALSE,
                   title="Effects of Social & Environmental Variables on General Wildlife Conflict")

##### Model Table of Effect Size:
sjPlot::tab_model(post.pa.full)

# Formatted Table (with labels):
# Notes: predictor labels (pred.labels) should be listed from top to bottom; dv.labels= the name of the response variable that will be at the top of the table.

post1.effects.tab <- sjPlot::tab_model(post.pa.full, 
                  show.re.var= TRUE, show.se = TRUE , show.p = TRUE , show.r2 = TRUE, show.aic = TRUE , 
                  pred.labels =c("(Intercept)" , "Distance to Protected Area (km)", "Distance to Metro Area (km)", "Animal & Meat Farming", "Ground Crop & Produce Farming", "Population Density"),
                                 dv.labels= "Effects of Social & Environmental Variables on Wildlife Conflict")

```


## Find the Area Under the Curve for our Posterior Distributions:
```{r roc plot, echo=FALSE}
# Plot ROC for the Simple Posterior:
par(pty="s") # sets our graph to square
roc(conflict_presence_ps, post.pa.full$fitted.values, plot=TRUE, legacy.axes=TRUE, percent=TRUE ,
    xlab= "False Positive Percentage", ylab= "True Positive Percentage",
    col="#377eb8", lwd=4, print.auc=TRUE) # this gives us the ROC curve , in 3544 controls (bears 0) < 2062 cases (bears 1), Area under curve = 0.

# Add ROC curve for our full pseudo-abs model:
plot.roc(conflict_presence_ps, post.int.only$fitted.values, percent=TRUE, col='#4daf4a', lwd=4, print.auc=TRUE, add=TRUE, print.auc.y=60)

legend("bottomright", legend=c("Full Pseudo-abs Regression", "Null Pseudo-abs Regression"),
       col=c("#377eb8", "#4daf4a"), lwd = 4)
```
Comparing the simple pseudo-absence model with the full model in a ROC plot shows that the full model has a 88% discrimination. This indicates that the model predictions are correct 88% of the time, slightly better than the null model at 87%.


## Leave One Out Cross Validation:
```{r LOO, echo=FALSE}
# Leave-one-out Cross_validation: -----------------------------------------
# Run a Leave-One-Out (LOO):
# Loo package implements fast Pareto smoothed leave-one-out-cross-val (PSIS-LOO) to compute expected log predictive density:
(loo.simplest <- loo(post.pa.simplest, save_psis = TRUE))
# Above we see that PSIS-LOO result is reliable as all Pareto k estimates are small (k< 0.5) Vehtari, Gelman and Gabry (2017a).

(loo.pa.full <- loo(post.pa.full, save_psis = TRUE))


plot(loo.pa.full, label_points = TRUE)
loo.pa.full # get the summary of our test

############## Comparison to Baseline Model: -------------------------------------------

# Compute our baseline result without covariates:
post0.ps <- update(post.int.only, formula = bears_presence_ps ~ 1 + (1 | CCSNAME.ps), QR = FALSE, refresh=0)

# Compare to our baseline:
(loo.0.ps <- loo(post0.ps)) # computing the PSIS-LOO for our baseline model

loo.comparison.ps <- loo_compare(loo.0, loo.pa.comp, loo.pa.full) # this high negative value for post0 shows us the covariates contain clearly useful information for predictions
loo.comparison.ps
```
We conduct a leave-one-out cross validation for our three models and then compare them to the zero posterior. Above, we see that the full model and simple model's PSIS-LOO result is reliable as all Pareto k estimates are small (k< 0.5) and the Monte Carlo SE is 0.1 (Vehtari, Gelman and Gabry 2017a). The null model is also reliable as it has a Monte Carlo SE of 0.0 and all Pareto k estimates are small (k< 0.5). Comparing these LOO values to our baseline, we see that the theoretical expected log point wise predictive density (elpd_loo) is lowest for our full model (still lower than the compare model) and highest for our baseline posterior (null model), indicating that the increased covariates in our models contain clearly useful information for predictions.

## K-Fold Cross Validation:
```{r K fold cross validate, echo=FALSE}
# K Fold Cross Validation: -----------------------------------------
# Setting up a K - fold cross validation for our general model: 

# (if possible also specify the 'cores' argument to use multiple cores) 
kfold.10.ps <-kfold(post.pa.full, K=10, cores = getOption("mc.cores", 1), save_fits = TRUE)
kfold.10.ps.int <- kfold(post.int.only, K=10, cores = getOption("mc.cores", 1))

# Try a stratified k-fold, stratifying on the CCSID variable:
cv10folds.ccs <- kfold_split_stratified(K=10, x=mini.warp.df.ps$CCSNAME.ps)

# Save this as data:
saveRDS(kfold.10.ps, file = "/Users/shannonspragg/ONA_GRIZZ/Data/processed/post_pa_kfold10.rds")
saveRDS(kfold.10.ps.int, file = "/Users/shannonspragg/ONA_GRIZZ/Data/processed/post_pa_kfold10_int.rds")

kfold.10.ps <- readRDS(file = "/Users/shannonspragg/ONA_GRIZZ/Data/processed/post_pa_kfold10.rds")
```

## Create our Varying Intercept Raster
```{r varying intercept raster, echo=FALSE}
# Bring in Data: ----------------------------------------------------------
soi.ccs.crop <- st_read( "/Users/shannonspragg/ONA_GRIZZ/Data/processed/SOI_CCS_10km.shp")
  # Bring in one of our rasters for rasterizing polygon data later:
soi.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/SOI_10km.tif") # SOI Region 10km

# Reproject the Data:
soi.ccs.reproj <- st_make_valid(soi.ccs.crop) %>% 
  st_transform(crs=crs(soi.rast))

# Check to see if they match:
st_crs(warp.pres.abs) == st_crs(soi.ccs.reproj) # [TRUE] 

# Extracting CCS Varying Intercept from Posterior: ------------------------

  # Need to make the ranef(post.pa.full) into a dataframe and join by CCS name to our warp.pres.abs:
varying.int.means <- as.data.frame(ranef(post.pa.full))
vary.int.subset <- varying.int.means[ , c("grp", "condval")]

  # Join the tab data with spatial:  
ccs.varint.join <- merge(soi.ccs.crop, vary.int.subset, by.x = "CCSNAME", by.y = "grp")

  # Now that it's spatial, do a spatial join to assign a varying intercept mean to each point:
warp.varint.join <- st_join(warp.pres.abs, left = TRUE, ccs.varint.join) # join points

  # Clean this up
warp.varint.join$PRNAME <- NULL
warp.varint.join$PRNTCDVSNC <- NULL
warp.varint.join$PRUID <- NULL
warp.varint.join$CDUID <- NULL
warp.varint.join$CPRVNCCD <- NULL
warp.varint.join$FTRCD <- NULL
warp.varint.join$CPRVNCCD <- NULL
warp.varint.join$PRNTCDVSNC <- NULL
warp.varint.join$FFCTVDT <- NULL
warp.varint.join$XPRDT <- NULL
warp.varint.join$OBJECTID <- NULL
warp.varint.join$AREA_SQM <- NULL
warp.varint.join$FEAT_LEN <- NULL 
warp.varint.join$CDNAME <- NULL
warp.varint.join$CDTYPE <- NULL
warp.varint.join$CPRVNCNM <- NULL
warp.varint.join$CCSNAME.y <- NULL
warp.varint.join$CCSUID.y <- NULL
warp.varint.join$CCSUID_ <- NULL
  
# Rename these quick:
names(warp.varint.join)[names(warp.varint.join) == "CCSNAME.x"] <- "CCSNAME"
names(warp.varint.join)[names(warp.varint.join) == "CCSUID.x"] <- "CCSUID"
names(warp.varint.join)[names(warp.varint.join) == "condval"] <- "CCS_Varying_Int"

# Make our CCS Raster: ----------------------------------------------------
  # Make these spatvectors:
soi.ccs.sv <- vect(soi.ccs.reproj)
warp.ps.sv <- vect(warp.varint.join)

# Make our CCS Post Mean Raster: ------------------------------------------
soi.ccs.rast <- terra::rasterize(soi.ccs.sv, soi.rast, field = "CCSNAME")

# Make Raster for our Posterior Means for CCS Varying Intercept: ---------------------
varint.means.rast <- terra::rasterize(warp.ps.sv, soi.rast, field = "CCS_Varying_Int")
names(varint.means.rast)[names(varint.means.rast) == "OBJECTID"] <- "CCS Varying Intercept Mean Estimate"

  # Extract Values of Posterior Means to CCS regions: 
warp.varint.mean.ext <- terra::extract(varint.means.rast, soi.ccs.sv, mean, na.rm = TRUE) 

  # Create New Column(s) for Extracted Values:
soi.ccs.sv$CCSMean <- warp.varint.mean.ext[,2] 

# Make our CCS Post Mean Raster: ------------------------------------------
ccs.varint.means.rast <- terra::rasterize(soi.ccs.sv, soi.rast, field = "CCSMean")
names(soi.ccs.rast)[names(soi.ccs.rast) == "PostMean"] <- "CCS Varying Intercept Means"

  # Check this:
plot(ccs.varint.means.rast) 

# Save our CCS Post Means Raster: -----------------------------------------
terra::writeRaster(ccs.varint.means.rast, "/Users/shannonspragg/ONA_GRIZZ/Data/processed/CCS_varint_raster.tif" )
ccs.varint.means.rast <- rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/CCS_varint_raster.tif")
```


## Bring in Predictor Rasters:
```{r bring in data 2, echo=FALSE, include=FALSE}
# Here we bring in all of our predictor rasters for the SOI region:
  # link to data here:   https://drive.google.com/drive/u/0/folders/1T60Al9vHOF-E7ftKzvzN2CMUyF1agC-l

  # Distance to Neartest Protected Area (km):
dist2pa.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/dist2pa_SOI_10km.tif" )
#dist2pa.inv.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/dist2pa_Sinvert_raster.tif" )

  # Distance to Nearest Metro Area (km):
dist2met.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/dist2metro_raster.tif" )
#dist2met.inv.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/dist2metro_invert_raster.tif" )

  # Animal & Meat Farming Density:
animal.farming.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/animal_production_density_raster.tif")

  # Ground Crop & Produce Production Density:
ground.crop.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/ground_crop_density_raster.tif")

  # Human Pop Density (by sq km):
hm.dens.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/human_dens_SOI_10km.tif") # SOI Region 10km

  # CCS Region ID:
ccs.varint.rast <- terra::rast("/Users/shannonspragg/ONA_GRIZZ/Data/processed/CCS_varint_raster.tif" )
```

## Scale Predictor Rasters:
```{r scale our variables, echo=FALSE}
# Scale the Rasters:
# We can do this Step by Step:

# Distance to PA: (using inverted rasters)
d2pa.mean <- mean(warp.pres.abs$dst__PA)
d2pa.sub.mean <- dist2pa.rast - d2pa.mean
d2pa.sd <- sd(warp.pres.abs$dst__PA)
dist2pa.rast.sc <- d2pa.sub.mean / ( 2 * d2pa.sd)

# Distance to Metro
d2met.mean <- mean(warp.pres.abs$dst_t_M)
d2met.sub.mean <- dist2met.rast - d2met.mean
d2met.sd <- sd(warp.pres.abs$dst_t_M)
dist2metro.rast.sc <- d2met.sub.mean / ( 2 * d2met.sd)

# Animal Farm Density:
animal.farm.mean <- mean(warp.pres.abs$Anml_Fr)
anim.f.sub.mean <- animal.farming.rast - animal.farm.mean
anim.f.sd <- sd(warp.pres.abs$Anml_Fr)
animal.farm.rast.sc <- anim.f.sub.mean / ( 2 * anim.f.sd)

# Ground Crop Density:
ground.crop.mean <- mean(warp.pres.abs$Grnd_Cr)
ground.c.sub.mean <- ground.crop.rast - ground.crop.mean
ground.c.sd <- sd(warp.pres.abs$Grnd_Cr)
ground.crop.rast.sc <- ground.c.sub.mean / ( 2 * ground.c.sd)

# Human Density:
pop.dens.mean <- mean(warp.pres.abs$Human_Dens)
pop.sub.mean <- hm.dens.rast - pop.dens.mean
pop.dens.sd <- sd(warp.pres.abs$Human_Dens)
hm.dens.rast.sc <- pop.sub.mean / ( 2 * pop.dens.sd)
```
Here, we scale our predictor rasters just like we scaled our variables. We scale each raster by the corresponding predictor value for mean and standard deviation that the predictor variable data was scaled with.

## Creating Probability of General Conflict Raster:

Here we use the coefficients resulting from the above full regression to preform raster math (coeff_1 * predictor raster + coeff_2 * predictor raster + ...) to create one condensed raster representing the probability of general conflict.

```{r raster math, echo=FALSE, include=TRUE}
# Make sure extents match:
ext(dist2pa.rast.sc) == ext(dist2metro.rast.sc) # TRUE
ext(dist2metro.rast.sc) == ext(animal.farm.rast.sc) #TRUE
ext(ground.crop.rast.sc) == ext(hm.dens.rast.sc) #TRUE

# View our Full Model Coefficients:
summary(post.pa.full)
fixef(post.pa.full)

# Stack these spatrasters:
conf.rast.stack <- c(dist2pa.rast.sc, dist2metro.rast.sc, animal.farm.rast.sc, ground.crop.rast.sc, hm.dens.rast.sc, ccs.varint.rast)
plot(conf.rast.stack) # plot these all to check


# Create P(all conflict) raster with our regression coefficients and rasters:
    # Prob_conf_rast = Int.val + CCS + B_1est * PopDens…
conflict_rast <- -1.48500922 + ccs.varint.rast + (-0.65376870 * dist2pa.rast.sc) + (-1.44075814 * dist2metro.rast.sc) + (2.11855439 * animal.farm.rast.sc) + (0.03700273 * ground.crop.rast.sc) + (0.67683370 * hm.dens.rast.sc) 

# Convert the Raster to the Probability Scale:
p_conf_rast <- app(conflict_rast, fun=plogis)

plot(p_conf_rast)
```
We use raster math calculations to apply the regression coefficients to each corresponding raster and add these together to produce our probability of general wildlife conflict raster.

```{r write raster}
# Save our P(General Conflict) Raster:
terra::writeRaster(p_conf_rast, "/Users/shannonspragg/ONA_GRIZZ/Data/processed/prob_general_conf_inv.tif")
```
Next, we can extract the values of this raster to our original warp conflict report data frame (1's = bears, 0's = other species reports), to use the p(general conlfict) as a predictor in the second Bayes model of bear conflict.




